\documentclass[apaper,20pt]{article}
\def\labelitemi{$\circ$}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome5} % for using icons
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx} % for reflecting the phone icon

% Define custom colors
\definecolor{primaryColor}{RGB}{0, 79, 144}
\newcommand{\colorBoxBlue}[1]{\colorbox[RGB]{0,191,255}{#1}}
\newcommand{\colorBoxMustard}[1]{\colorbox[RGB]{255,187,0}{#1}}
\newcommand{\colorBoxGreen}[1]{\colorbox[RGB]{93,226,60}{#1}}

% Hyperlink settings
\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Resume},
    pdfpagemode=FullScreen,
}
\newcommand{\MYhref}[3][primaryColor]{\href{#2}{{\color{#1}#3}}}

% Page style adjustments
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Nikhil Sharma} \\ \vspace{5pt}
    \MYhref{tel:+918968491353}{\reflectbox{\faPhone}\ +91-8968491353} \quad  
    \MYhref{https://maps.app.goo.gl/rMSBQRqs4LkHJ8Jf6}{\faMapMarker*\ Chandigarh, India} \\ \vspace{5pt}
    \MYhref{mailto:nikhils.sharma2409@gmail.com}{\faEnvelope\ nikhils.sharma2409@gmail.com} \quad 
    \MYhref{https://github.com/itsnikhil24}{\faGithub\ github.com/itsnikhil24} \quad 
    \MYhref{https://www.linkedin.com/in/nikhil-sharma-487837290/}{\faLinkedin\ linkedin.com/in/itsnikhil24}    
\end{center}
\vspace{-6pt}

\section{Experience}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeSubheading
{Diskovalist}{Remote}
{IT Intern }{June 2025 - Present}
\begin{itemize}

   \item {Developed full-stack features using Next.js, TypeScript, and PostgreSQL, building reusable APIs and structured schemas to streamline frontend–backend integration.}
\item {Implemented robust schema validation with Zod and custom React hooks, improving code reusability, type safety, and maintainability across the project.}
\item {Automated data extraction workflows by parsing PDFs with regex and storing structured records in PostgreSQL, enhancing efficiency of data management processes.}


\end{itemize}
\vspace{-10pt}







% \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading
{Beyond Career}{Remote}
{SDE Intern }{February 2025 - March 2025}
\begin{itemize}

    \item {Implemented Google Sign-In authentication on login and registration pages, enhancing user onboarding experience and security.}
	\item { Organized the codebase using the MVC (Model-View-Controller) pattern, ensuring better scalability and maintainability.}
	\item {Designed and developed RESTful APIs using Node.js and Express.js, enabling seamless communication between frontend interfaces and backend services.}
\end{itemize}

% \resumeItemListEnd
\resumeSubHeadingListEnd


%----------PROJECTS-----------------
\section{Projects}


\resumeSubHeadingListStart

\resumeSubheading
  {\MYhref{https://github.com/itsnikhil24/New_Chatapp.git}{ChatSphere}} 
  {January 2025} 
  {HTML, CSS, JavaScript, Node.js, Express, MongoDB} 
  {}


\resumeItemListStart
    \item \textbf{Emphasis:} ChatSphere is a real-time chat app using Node.js, Express, and Socket.IO for instant messaging. It features JWT authentication, MongoDB storage, Cloudinary media sharing, and an MVC architecture for scalability.
    \item \textbf{Features:} Utilized technologies such as EJS, CSS, and JavaScript to create a responsive and user-friendly interface.
    \begin{itemize}
        \item Real-Time Messaging – Powered by Socket.IO, users can send and receive messages instantly.
        \item Room-based Chat – Users can join specific chat rooms for focused discussions
        \item Express.js Backend – Built with MVC architecture for clean and scalable code.
    \end{itemize}
\resumeItemListEnd

\resumeSubheading{\MYhref{https://github.com/itsnikhil24/Floodmanagement.git}{Farm Flood Aid} \MYhref[red]{https://flood-management-website.vercel.app/}{[Website]}}{October 2024}{HTML, CSS, JavaScript, Node.js, Express, MongoDB}{}

\resumeItemListStart
    \item \textbf{Emphasis:} Developed and deployed a Flood Management website to assist farmers in Myanmar during severe flood conditions. Implemented features like a chatbot for support, a marketplace for surplus crop sales, and NGO contact information.
    \item \textbf{Features:} Utilized technologies such as HTML, CSS, and JavaScript to create a responsive and user-friendly interface.
    \begin{itemize}
        \item Implemented a chatbot to provide real-time assistance on flood management, waterlogging reduction, and contact information.
        \item Designed a marketplace for farmers to sell surplus crops, reducing wastage and fostering collaboration with NGOs.
        \item Integrated NGO contact information to ensure farmers can easily access aid and support during emergencies.
    \end{itemize}
\resumeItemListEnd




\resumeSubHeadingListEnd

%-----------SKILLS--------------------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{C, C++, JavaScript, Python}
\resumeSubItem{Tools}{Git, GitHub Actions, Google Cloud, MongoDB, MySQL, AWS, Firebase, Supabase}
\resumeSubItem{Frameworks/Libraries}{Node.js, Express, React}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
\item Community Impact Award Winner at the Myanmar Flood Response Hackathon hosted on Devpost for the project "FarmFloodAid".
\item HackerRank level 5 C++ Programmer.
{\MYhref{https://www.hackerrank.com/nikhils_sharma21}{HackerRank Profile}}
\item Postman Fundamental Student Expert.
\item Google Cloud Arcade Program Participant: Completed 150 labs in the Google Cloud Arcade program.
\item Attained the badge of {\MYhref{https://www.cloudskillsboost.google/public_profiles/158ff43d-244d-49d7-9269-b6014d626472}{Google Cloud Skill badge}}.
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Chandigarh University}{Mohali, Punjab}{Bachelor of Engineering - Computer Science; CGPA: 8.77}{September 2023 -- Expected June 2027}
\resumeSubheading{Govt. Model Sr. Sec School, 37-B}{Chandigarh}{Secondary School Education (Science); Percentage: 76}{July 2021 -- May 2023}
\resumeSubheading{Stepping Stones Sr. Sec. School, 37-D}{Chandigarh}{High School Education; Percentage: 89.9}{July 2007 -- April 2021}
\resumeSubHeadingListEnd

\end{document}
